\problemname{\problemyamlname}

%\illustration{0.3}{image.jpg}{CC-BY 2.0 By X on Y}
% Source: URL to image.

% optionally define variables/limits for this problem
\newcommand{\minn}{3}
\newcommand{\maxn}{500}
\newcommand{\minm}{3}
\newcommand{\maxm}{500}

Going to the movies is great, and it's even better if you don't have to cross the hall with popcorn and cola in your hands.

You are visiting a movie theater, which has a form of a rectangle with entrances, exits and available seats. You would like to enter the theater, get into some seat and leave, while covering as low distance as possible. What is the shortest distance that you must cover?

Movie theater plan is represented as a two-dimensional grid of characters:
\begin{itemize}
    \item Entrances are located on the sides and are marked with letter E.
    \item Exits are located on the sides and are marked with letter X.
    \item Seats are located in the center (not on the side) and are marked with letter S.
    \item There is at least one entrance, one exit and one seat.
    \item Remaining empty space is filled with dot symbols.
\end{itemize}

\begin{Input}
    The input consists of multiple lines:
    \begin{itemize}
        \item First line contains two integers $n$ and $m$ ($\minn \leq n \leq \maxn$, $\minm \leq m \leq \maxm$), the dimensions of the grid.
        \item The following $n$ lines describe the movie theater. Every line contains $m$ characters, each being E, X, S or a dot.
     \end{itemize}
\end{Input}

\begin{Output}
    Print one integer number: the shortest distance you could cover from an entrance to an exit through a seat.
\end{Output}
